---
title       : Power to the People
subtitle    : An friendly tool for power calculations
author      : Phil Allen
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft, selfcontained}
knit        : slidify::knit2slides
---

```{r, warning=FALSE,message=FALSE,results='hide', echo=FALSE}
library(dplyr)
library(lubridate)
library(spatstat)
library(ggplot2)
```

## Power is hard

* Often, study designers hoping to see an effect
* Thinking about _not_ finding it is unntuitive
* Can lead to wasted studies

---

## Make it easier

* Concentrate on key use cases:
  + Find effect size at acceptable power
  + Find group size you need
* Provide a visualisation

---

## Simple visualisation

* Thanks to Brian Caffo 
* Visualisation actually shows Z-test, but results from power.t.test
* Effect size (x-axis) 0.5, and group size 20

```{r simplevis, echo=FALSE, message=FALSE, fig.height=4}
pow_plot <- function(effect_size, n, alpha){
  g = ggplot(data.frame(effect_size = c(-2, 3)), aes(x = effect_size))
  g = g + stat_function(fun=dnorm, geom = "line", 
                        args = list(mean = 0, sd = 1 / sqrt(n)), 
                        size = 2, col = "red")
  g = g + stat_function(fun=dnorm, geom = "line", 
                        args = list(mean = effect_size, sd = 1 / sqrt(n)), 
                        size = 2, col = "blue")
  xitc = qnorm(1 - alpha) / sqrt(n)
  g = g + geom_vline(xintercept=xitc, size = 1)
  # p <- pnorm(xitc, mean = effect_size, sd = 1 / sqrt(n), lower.tail = FALSE)
  p <- power.t.test(n=n, delta=effect_size, sd=1, type="one.sample", alt="one.sided")$power
  g <- g + ggtitle(paste0("power: ", round(p,3))) + xlab("Effect size")
  g
}
pow_plot(0.5,20,0.05)
```


