---
title       : Power to the People
subtitle    : An friendly tool for power calculations
author      : Phil Allen
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft, selfcontained}
knit        : slidify::knit2slides
---

```{r, warning=FALSE,message=FALSE,results='hide', echo=FALSE}
library(dplyr)
library(lubridate)
library(spatstat)
library(ggplot2)
```

## Power is hard

* Often, study designers hoping to see an effect
* Thinking about _not_ finding it is unntuitive
* Can lead to wasted studies

---

## Make it easier

* Concentrate on key use cases:
  + Find effect size at acceptable power
  + Find group size you need
* Provide a visualisation

---

## Simple visualisation

* Thanks to Brian Caffo 
* Visualisation actually shows Z-test, but results from power.t.test
* Effect size (x-axis) 0.5, and group size 20, with alpha 0.05

```{r simplevis, echo=FALSE, message=FALSE, fig.height=4}
source("pres.R")
pow_plot(effect_size=0.5, n=20, alpha=0.05, objective="Power")
```


